TODO

### 2024-12-13 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
ran models

library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(here)
library(brms)
library(rstan)
library(rstanarm)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

@@

# experiment 1 imports
transcript_1 <- read_csv(here(expt_1,"timed_transcript.csv"))
dat_1 <- read_csv(here(expt_1, "clean_data.csv")) |> rename(trial=trialNum)
exclusion_1 <- transcript_1 %>% filter(!is.na(description)) %>% filter(role=="S") %>% select(game,  echo,) %>% unique() %>% mutate("S_talked"=1)

@@

# sims_1 <- read_rds(here(expt_1,"similarities.rds")) |> 
#     as_tibble() 
#   inner_join(clean_1|> select(game1 = game, trial1 = trial, target1 = target, speaker1 = speaker)) |>
#   inner_join(clean_1 |> select(game2 = game, trial2 = trial, target2 = target, speaker2 = speaker)) |>
#   filter(target1 == target2) |>
#   mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |> 
#   mutate(same_speaker=(speaker1==speaker2) |> as.numeric(),
#          same_game=(game1==game2) |> as.numeric(),
#         later = ifelse(block1 > block2, block1, block2), 
#         earlier = ifelse(block1 > block2, block2, block1)) |> mutate(target=target1)

@@

# sims_2 <- read_rds(here(expt_2, "similarities.rds")) |>
#   as_tibble() |>
#   inner_join(clean_2 |> select(game1 = gameId, trial1 = trial, target1 = target, speaker1 = speaker)) |>
#   inner_join(clean_2 |> select(game2 = gameId, trial2 = trial, target2 = target, speaker2 = speaker)) |>
#   filter(target1 == target2) |>
#   mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |> 
#   mutate(same_speaker=(speaker1==speaker2) |> as.numeric(),
#          same_game=(game1==game2) |> as.numeric(),
#         later = ifelse(block1 > block2, block1, block2), 
#         earlier = ifelse(block1 > block2, block2, block1)) |> mutate(target=target1)
```

@@

* Rerun [re-processing 
sbert stuff

* Run models

* Double check pre-regs and note deviations

@@

* get age range mean and gender distributions!

* mention that we post-hoc excluded trials where we couldn't transcript any speaker description (either didn't happen or completely unintelligible)

# Pre-regs
https://osf.io/kcv8j

https://osf.io/y2dax

Analyses -- Expt 1

This is exploratory research, and we will explore the following questions graphically:
* how accurate are children over time
* how many words of description does the speaker produce over time
* do children speed up in their selections over time
* do children match the descriptions their partner uses

We will also analyze the transcripts to look at children’s turn-taking structure and how they understand each other.

We plan to run the model:
DV  ~ trial_num + (trial_num|dyad) + (1|target) 
for the DVs: 
[x] accuracy (logistic model), 
[ ] speed (linear model) and 
[ ] number of words of speaker description (linear model ).

Analyses -- Expt 2

Primarily, we aim to replicate the results of experiment 1, using the following models.

[x] Logistic model of accuracy: correct ~ trialNum + (trialNum|game) + (1|target) (prior normal(0,1) for beta and sd, lkj(1) for correlation)

[ ] Linear model of description length: words ~ trialNum + (trialNum|game) + (1|target) (prior intercept of normal(5,10), beta and sd priors of normal(0,5), and correlation of lkj(1))

[ ] Speed: time_seconds ~ trialNum + (trialNum|game) + (1|target) (prior intercept of normal(60,100), beta and sd priors of (0,20) and correlation of lkj(1))

We will interpret the fixed effect of trial number as being about changes in referring over time.

For utterance similarities, we will embed the describer’s descriptions using S-BERT and use cosine similarity as a proxy for utterance similarity.

We are unsure whether 4 blocks will be sufficient to see potential change over time, so we will 
[ ] * compare similarities of utterances between different games v within one game v within one speaker: sim ~ same_game + same_speaker + (1|target) 
[ ] * compare similarities of utterances to the last utterance within a game: sim_to_last ~ earlier_block + same_speaker + (1|game) + (1|target)
[ ] * compare similarities of utterances to the next utterance: sim_to_next ~ earlier_block + same_speaker + (1|game) + (1|target)
[ ] * compare the similarity level of descriptions from the same block in different games: sim ~ block + (1|target)
Priors for the above similarity models: normal(.5,.2) for intercept, normal(0,.1) for
beta, and normal(0,.05) for sd.

We will also qualitatively explore children’s turn-taking structure and how they understand each other.

@@

TODO link to pre-registration

## Participants
4 and 5 year old children were recruited from a university nursery school during the school day. Children played with another child from the same class. TODO any exclusions Experiment 1 was conducted between June and August 2023. Children were only included in analysis if they completed at least 8 of the critical trials. We had XX complete games and YY incomplete, but included games.

@@

@@

```{r}
acc_priors <- c(
set_prior("normal(0,1)", class="b"),
set_prior("normal(0,1)", class="sd"),
set_prior("lkj(1)", class="cor")
)

acc_mod_data <- clean_1 |> mutate(correct.num=ifelse(correct==TRUE, 1,0),
                                  trial.num=trial-2) |> filter(type!="practice")
acc_mod <- brm(correct.num ~ trial.num + (trial.num|game) + (1|target),
               family = bernoulli(link = "logit"),
               data=acc_mod_data,
               file = here(mod_loc, "acc_1.rds"),
               prior=acc_priors,
               control = list(adapt_delta=.95))
```

@@

@@

@@

```{r, fig.width=4, fig.height=3}

# sims_1 %>%  filter(!is.na(sim)) %>% 
#   filter(!trial1 %in% c("0","1")) %>% filter(!trial2 %in% c("0","1"))%>% #not practice
#   left_join(labels1) %>% left_join(labels2) %>%
#   mutate(same_target=ifelse(target1==target2, "Same target", "Different target"),  #label if target is same or not
#   same_child=case_when(
#     game1!=game2 ~ "Different\n games",
#     (as.numeric(trial1)-as.numeric(trial2))%%2==1~"Different\n speaker", #children alternate
#     T ~"Same\n speaker"),
#   type1=case_when(trial1<2 ~ "practice",
#                         trial1<6 ~ "block 1",
#                         trial1<10 ~ "block 2",
#                         trial1<14 ~ "block 3"),
#          type2=case_when(trial2<2 ~ "practice",
#                         trial2<6 ~ "block 1",
#                         trial2<10 ~ "block 2",
#                         trial2<14 ~ "block 3")) %>% 
#   filter(type1!=type2) %>% # can only compare across blocks in some cases, so only cross ever
#     mutate(blocks=case_when(
#       type1=="block 1" & type2=="block 2"~ "Block 1 v 2   ",
#       type1=="block 2" & type2=="block 1"~ "Block 1 v 2   ",
#       type1=="block 1" & type2=="block 3"~ "Block 1 v 3   ",
#       type1=="block 3" & type2=="block 1"~ "Block 1 v 3   ",
#       type1=="block 2" & type2=="block 3"~ "Block 2 v 3   ",
#       type1=="block 3" & type2=="block 2"~ "Block 2 v 3   "
#       )) %>%
#   ggplot(aes(x=str_c(same_child), y=sim, color=blocks)) +
#   facet_grid(.~same_target) +
#   theme_bw()+
#   #geom_jitter(alpha=.01, color="black") +
#   labs(x="", y="Cosine similarity", color="")+
#   scale_color_brewer(type="qual", palette="Dark2")+
#   scale_y_continuous(limits=c(0,1), expand=c(0,0))+
#       stat_summary(fun.data="mean_cl_boot", geom="pointrange", position=position_dodge(width=.2))+
#     guides( color = guide_legend( override.aes = list(linetype=0, size=1)))+
#   theme(strip.background =element_rect(fill="white"),
#         legend.position="bottom",
#         axis.title.x=element_blank())

@@

```{r}
# sims_1 %>%  filter(!is.na(sim)) %>% 
#   filter(!trial1 %in% c("0","1")) %>% filter(!trial2 %in% c("0","1"))%>% #not practice
#   left_join(labels1) %>% left_join(labels2) %>%
#   mutate(same_target=ifelse(target1==target2, "same_target", "diff_target"),  #label if target is same or not
#   same_child=case_when(
#     game1!=game2 ~ "diff game",
#     (as.numeric(trial1)-as.numeric(trial2))%%2==1~"diff_child", #children alternate
#     T ~"same_child"),
#   type1=case_when(trial1<2 ~ "practice",
#                         trial1<6 ~ "block 1",
#                         trial1<10 ~ "block 2",
#                         trial1<14 ~ "block 3"),
#          type2=case_when(trial2<2 ~ "practice",
#                         trial2<6 ~ "block 1",
#                         trial2<10 ~ "block 2",
#                         trial2<14 ~ "block 3")) %>% 
#   filter(type1==type2) %>% # can only compare across blocks in some cases, so only cross ever
#   ggplot(aes(x=str_c(same_target,"\n",same_child), y=sim, color=type1)) +
#   geom_jitter(alpha=.01, color="black") +
#       stat_summary(fun.data="mean_cl_boot", geom="pointrange", position=position_dodge(width=.2))+
#   labs(x="Conditions compared")
```

# Experiment 1 Discussion

@@

As Experiment 2 was very similar to Experiment 1, here we note the differences.

## Participants
Experiment 2 was run between March and August of 2024, at the same university preschool. No children participated in both experiments. ZZ pairs of children completed all 16 critical trials, and YY pairs of children completed between 8 and 16 critical trials. TODO mention that one kid was actually too young

@@

```{r}
acc_priors <- c(
set_prior("normal(0,1)", class="b"),
set_prior("normal(0,1)", class="sd"),
set_prior("lkj(1)", class="cor")
)

@@

@@

@@

```{r}
# sims_2 |>
#   mutate(source = case_when(
#     speaker1 == speaker2 ~ "same speaker",
#     game1 == game2 ~ "same game",
#     T ~ "different games"
#   )) |>
#   ggplot(aes(x = source, y = sim, color = target1)) +
#   stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
#   labs(y = "Cosine similarity", x = "Comparing two utterances from ...", color = "target image") +
#   theme(legend.position = "bottom")

@@

```{r}
# sims_2 |>
#   filter(game1 == game2) |>
#   mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
#   filter(later == 4) |>
#   mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
#   ggplot(aes(as.character(earlier), sim, color = target1)) +
#   geom_point(alpha = .1, position = position_dodge(width = .2)) +
#   stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
#   facet_wrap(~same_speaker) +
#   labs(x = "Earlier block to last block", y = "cosine similarity", color = "target") +
#   theme(legend.position = "bottom")
```

```{r}
# sims_2 |>
#   filter(game1 == game2) |>
#   mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
#   filter(later == earlier + 1) |>
#   mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
#   ggplot(aes(as.character(earlier), sim, color = target1)) +
#   geom_point(alpha = .1, position = position_dodge(width = .2)) +
#   stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
#   facet_wrap(~same_speaker) +
#   labs(x = "Earlier block to *next* block", y = "cosine similarity", color = "target") +
#   theme(legend.position = "bottom")
```

```{r}
# sims_2 |>
#   filter(game1 != game2) |>
#   mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
#   filter(later == earlier) |>
#   ggplot(aes(as.character(earlier), sim, color = target1)) +
#   geom_point(alpha = .01, position = position_dodge(width = .2)) +
#   stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
#   labs(x = "Cross game similarity in block ...", y = "cosine similarity", color = "target") +
#   theme(legend.position = "bottom")
```

>>>>

library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(here)
library(brms)
library(rstan)
library(rstanarm)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

# experiment 1 imports
transcript_1 <- read_csv(here(expt_1,"timed_transcript.csv"))
dat_1 <- read_csv(here(expt_1, "clean_data.csv")) |> rename(trial=trialNum)
exclusion_1 <- transcript_1 %>% filter(!is.na(description)) %>% filter(role=="S") %>% select(game, trial) %>% unique() %>% mutate("S_talked"=1)

@@

sims_1 <- read_rds(here(expt_1,"similarities.rds")) |>
    as_tibble() |> 
  inner_join(clean_1|> select(game1 = game, trial1 = trial, target1 = target, speaker1 = speaker)) |>
  inner_join(clean_1 |> select(game2 = game, trial2 = trial, target2 = target, speaker2 = speaker)) |>
  filter(target1 == target2) |>
  filter(trial1>1) |> 
  filter(trial2>1) |> 
  mutate(trial1=trial1+2,
         trial2=trial2+2) |> 
  mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |>
  mutate(same_speaker=(speaker1==speaker2) |> as.numeric(),
         same_game=(game1==game2) |> as.numeric(),
        later = ifelse(block1 > block2, block1, block2),
        earlier = ifelse(block1 > block2, block2, block1)) |> mutate(target=target1)

@@

sims_2 <- read_rds(here(expt_2, "similarities.rds")) |>
  as_tibble() |>
  inner_join(clean_2 |> select(game1 = gameId, trial1 = trial, target1 = target, speaker1 = speaker)) |>
  inner_join(clean_2 |> select(game2 = gameId, trial2 = trial, target2 = target, speaker2 = speaker)) |>
  filter(target1 == target2) |>
  mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |>
  mutate(same_speaker=(speaker1==speaker2) |> as.numeric(),
         same_game=(game1==game2) |> as.numeric(),
        later = ifelse(block1 > block2, block1, block2),
        earlier = ifelse(block1 > block2, block2, block1)) |> mutate(target=target1)
```

@@

* save model summaries

@@

* Experiment 1: do children match the descriptions their partner uses

* Experiment 1 + experiment 2: We will also analyze the transcripts to look at children’s turn-taking structure and how they understand each other.

@@

This experiment was pre-registered at https://osf.io/kcv8j.

## Participants
4 and 5 year old children were recruited from a university nursery school during the school day. Children played with another child from the same class. TODO any exclusions Experiment 1 was conducted between June and August 2023. Children were only included in analysis if they completed at least 8 of the critical trials. We had XX complete games and YY incomplete, but included games. TODO children's age range + median and gender split.

@@

We excluded trials where the child in the teller role did not produce a description, or where all description was unintelligible and impossible to transcribe.

@@

```{r, eval=F}
acc_priors <- c(
set_prior("normal(0,1)", class="b"),
set_prior("normal(0,1)", class="sd"),
set_prior("lkj(1)", class="cor")
)

acc_mod_data_1 <- clean_1 |> mutate(correct.num=ifelse(correct==TRUE, 1,0),
                                  trial.num=trial-2) |> filter(type!="practice")
acc_mod_1 <- brm(correct.num ~ trial.num + (trial.num|game) + (1|target),
               family = bernoulli(link = "logit"),
               data=acc_mod_data_1,
               file = here(mod_loc, "acc_1.rds"),
               prior=acc_priors,
               control = list(adapt_delta=.95))
```

@@

```{r, eval=F}

speed_priors <- c(
  set_prior("normal(60,100)", class="Intercept"),
set_prior("normal(0,20)", class="b"),
set_prior("normal(0,20)", class="sd"),
set_prior("lkj(1)", class="cor")
)

speed_mod_data_1 <- clean_1 |> mutate(time.sec=time/1000,
                                  trial.num=trial-2) |> filter(type!="practice")

speed_mod_1 <- brm(time.sec ~ trial.num + (trial.num|game) + (1|target),
               data=speed_mod_data_1,
               file = here(mod_loc, "speed_1.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))
```

@@

```{r, eval=F}

description_priors <- c(
  set_prior("normal(5,10)", class="Intercept"),
set_prior("normal(0,5)", class="b"),
set_prior("normal(0,5)", class="sd"),
set_prior("lkj(1)", class="cor")
)

description_mod_data_1 <- clean_1 |> mutate(
                                  trial.num=trial-2) |> filter(type!="practice")

description_mod_1 <- brm(words ~ trial.num + (trial.num|game) + (1|target),
               data=description_mod_data_1,
               file = here(mod_loc, "description_1.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))

@@

```{r}
sims_1 |>
  mutate(source = case_when(
    speaker1 == speaker2 ~ "same speaker",
    game1 == game2 ~ "same game",
    T ~ "different games"
  )) |>
  ggplot(aes(x = source, y = sim, color = target1)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  labs(y = "Cosine similarity", x = "Comparing two utterances from ...", color = "target image") +
  theme(legend.position = "bottom")

@@

```{r}
sims_1 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == 3) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |> 
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .1, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  facet_wrap(~same_speaker) +
  labs(x = "Earlier block to last block", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```

```{r}
sims_1 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier + 1) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .1, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  facet_wrap(~same_speaker) +
  labs(x = "Earlier block to *next* block", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```

```{r}
sims_1 |>
  filter(game1 != game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .01, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  labs(x = "Cross game similarity in block ...", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```
# Experiment 1 Discussion

@@

As Experiment 2 was very similar to Experiment 1, here we note the differences. Experiment 2 was pre-registered at https://osf.io/y2dax.

## Participants
Experiment 2 was run between March and August of 2024, at the same university preschool. No children participated in both experiments. ZZ pairs of children completed all 16 critical trials, and YY pairs of children completed between 8 and 16 critical trials. TODO mention that one kid was actually too young TODO mention age range / median and gender distribution.

@@

```{r, eval=F}
acc_priors <- c(
set_prior("normal(0,1)", class="b"),
set_prior("normal(0,1)", class="sd"),
set_prior("lkj(1)", class="cor")
)

@@

speed_priors <- c(
  set_prior("normal(60,100)", class="Intercept"),
set_prior("normal(0,20)", class="b"),
set_prior("normal(0,20)", class="sd"),
set_prior("lkj(1)", class="cor")
)

speed_mod_data_2<- clean_2 |> mutate(time.sec=time/1000,
                                  trial.num=trial-2) |> filter(type!="practice")

speed_mod_2 <- brm(time.sec ~ trial.num + (trial.num|gameId) + (1|target),
               data=speed_mod_data_2,
               file = here(mod_loc, "speed_2.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))
```

@@

```{r, eval=F}

description_priors <- c(
  set_prior("normal(5,10)", class="Intercept"),
set_prior("normal(0,5)", class="b"),
set_prior("normal(0,5)", class="sd"),
set_prior("lkj(1)", class="cor")
)

description_mod_data_2 <- clean_2 |> mutate(
                                  trial.num=trial-2) |> filter(type!="practice")

description_mod_2 <- brm(words ~ trial.num + (trial.num|gameId) + (1|target),
               data=description_mod_data_2,
               file = here(mod_loc, "description_2.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))
```

@@

```{r}
conv_priors <- c(
  set_prior("normal(.5,.2)", class="Intercept"),
set_prior("normal(0,.1)", class="b"),
set_prior("normal(0,.05)", class="sd")
)

sim_across_between_data_2 <- sims_2 |> 
mutate(same_game = case_when(
    game1 == game2 ~ 1,
    T ~ 0
  )) |>
    mutate(same_speaker = ifelse(speaker1 == speaker2, 1, 0))

sim_across_between_mod_2 <- brm(sim ~ same_game + same_speaker+ (1|target),
               data=sim_across_between_data_2,
               file = here(mod_loc, "sim_across_between_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

sim_to_last_data_2 <- sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == 4) |> 
    mutate(same_speaker = ifelse(speaker1 == speaker2, 1, 0),
           earlier_block.num=earlier-1)

sim_to_last_mod_2 <- brm(sim ~ earlier_block.num+ same_speaker+ (1|game1)+(1|target),
               data=sim_to_last_data_2,
               file = here(mod_loc, "sim_to_last_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

sim_to_next_data_2 <- sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier+1) |> 
    mutate(same_speaker = ifelse(speaker1 == speaker2, 1, 0),
           earlier_block.num=earlier-1)

sim_to_next_mod_2 <- brm(sim ~ earlier_block.num+ same_speaker+ (1|game1)+(1|target),
               data=sim_to_next_data_2,
               file = here(mod_loc, "sim_to_next_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

sim_across_data_2 <- sims_2 |>
  filter(game1 != game2) |>
  filter(block1 == block2) |> 
    mutate(block.num=block1-1)

sim_across_mod_2 <- brm(sim ~ block.num+(1|target),
               data=sim_across_data_2,
               file = here(mod_loc, "sim_across_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

@@

```{r}
sims_2 |>
  mutate(source = case_when(
    speaker1 == speaker2 ~ "same speaker",
    game1 == game2 ~ "same game",
    T ~ "different games"
  )) |>
  ggplot(aes(x = source, y = sim, color = target1)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  labs(y = "Cosine similarity", x = "Comparing two utterances from ...", color = "target image") +
  theme(legend.position = "bottom")

```{r}
sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == 4) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .1, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  facet_wrap(~same_speaker) +
  labs(x = "Earlier block to last block", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```

```{r}
sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier + 1) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .1, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  facet_wrap(~same_speaker) +
  labs(x = "Earlier block to *next* block", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```

```{r}
sims_2 |>
  filter(game1 != game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .01, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  labs(x = "Cross game similarity in block ...", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```
